---
title: "R Report 2"
author: "Oliver Hannaoui"
date: "5/27/2019"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
set.seed(10)
```

Simulating a binomial random variable. Considering a class of 80 students and that the probability that a student does not turn in a homework is 0.15. Assuming independence and no change in probability as well.

a) 
Using the sample function, the number of students who don't turn in their homework is 5.
```{r,echo=FALSE}
#1(a)
experiment = sample(c("X","F"),80,prob=c(0.15,0.85),replace=TRUE)
sum(experiment=="X")
```


b) 
Due to the fact that n>= 30 the distribution of the histogram is symmetric and has a normal shape.
```{r, echo = FALSE}
many.binom = sapply(1:1000000, function(i) { 
  binom = sample(c("X","F"), 80, 
                 prob = c(0.15, 0.85), replace = TRUE) 
  num.of.success = sum(binom == "X")
  return(num.of.success)
  })

hist1 = hist(many.binom, main = "Number of Students Who Don't Turn in Their Homework", xlab = "Students Who Don't Turn in Their Homework", ylab = "Frequency")
```

c)
The average and standard number of successes in 80 trials:
```{r, echo = FALSE}
#1(c)
mean(many.binom)
sd(many.binom)
```

d)
The probability that all students turn in their homework based on our simulation:
```{r, echo = FALSE}
#1(d)
prob1 = sum(many.binom == 0)
prob1/length(many.binom)
```

e) 
The probability that at least four students did not turn in their homework:
```{r, echo = FALSE}
#1(e)
prob3 = sum(many.binom >= 4)
prob3/length(many.binom)
```

f)
The median number of students who will forget their homework:
```{r, echo = FALSE}
#1(f)
median(many.binom)
```

II.
a) 
Data is used from built in "lynx" dataset.

The distribution of the histogram is skewed right.
```{r,echo=FALSE}
#2(a)
hist(lynx,main="Lynx Histogram",xlab="Heights")

```

Mean and Variance
```{r,echo=FALSE}
mean(lynx)
var(lynx)
```


b)
Mean of the random sample of 10.
```{r,echo=FALSE}
#2b
experiment = sample(lynx, 10, replace=TRUE)
mean(experiment)
```

c)
Mean and standard deviation of the 1000000 vector means.
```{r,echo=FALSE}
#2c
 many.experiments = sapply(1:1000000, function(i){
  experiment = sample(lynx,10, replace = TRUE)
  sample.mean= mean(experiment)
  return(sample.mean)
})
mean(many.experiments)
sd(many.experiments)
```


The distribution is slightly skewed right and the means are spread out in terms of frequency.
```{r,echo=FALSE}

hist(many.experiments, xlab='Means', main= 'Histogram of the Means')
```

d)
Mean of the sample size of 50:
```{r,echo=FALSE}
#2d
experiment = sample(many.experiments, 50, replace=TRUE)
mean(experiment)
```

e)
Mean stays approximately the same as before, however our standard deviation decreases substantially.
```{r,echo=FALSE}
#2e
 more.experiments = sapply(1:1000000, function(i){
  experiment = sample(many.experiments,50, replace = TRUE)
  sample.mean= mean(experiment)
  return(sample.mean)
})
mean(more.experiments)
sd(more.experiments)
```

f)
The distribution is approximately normally distributed and the means are a lot less spread out than our previous histogram, as the sample size increased our histogram become more normally distributed and our standard deviation decreased.
```{r, echo=FALSE}
#2f
hist(more.experiments, xlab='Means', main= 'Histogram of the Increased Sample Size')
```

Appendix:
```{r, ref.label=knitr::all_labels(),echo=TRUE,eval=FALSE}

```
